---
title: "Descubrimiento de subgrupos en el dataset *US Census Data*"
author: "Miruna Andreea Gheata, Miguel Rodríguez Gómez"
date: "3/16/2021"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
    df_print: paged
    number_sections: true
---

```{r}
#install.packages("dplyr")
library(dplyr) 
library(rsubgroup)
# install.packages("fst")
library(fst)
```

```{r}
data.filename = "USCensus1990.fst"
data <- read.fst("USCensus1990.fst")
```


```{r}
str(data)
```

- **Age**: Age Allocation Flag
- **Ancstry1**: First Ancestry Allocation Flag
- **Ancstry2**: Second Ancestry Allocation Flag
- **Avail**: Available for Work
- **Citizen**: Citizenship
- **Class**: Class of Worker
- **Depart**: Time of Departure for Work Hour and Minutes
- **Disabl1**:  Work Limitation Stat.
- **Disabl2**: Work Prevention Stat.
- **English**: Ability to Speak English
- **Feb55**: Served February 1955 July 1964
- **Fertil**: No. of Chld. Ever Born
- **Hispanic**: Detailed Hispanic Origin
- **Hour89**: Usual Hrs. Worked Per Week in 1989 Alloc
- **Hours**: Hrs. Worked Last Week Allocation Flag
- **Immigr**: Yr. of Entry
- **Income1**: Wages or Salary Inc. in 1989
- **Income2**: Nonfarm Self Employment Inc.
- **Income3**: Farm Self Employment Inc.
- **Income4**: Int., Dividends, and Net Rental Inc
- **Income5**: Soc. Sec Inc.
- **Income6**: Pub. Asst.
- **Income7**: Ret. Inc.
- **Income8**: All Other Inc.
- **Industry**: Ind.
- **Korean**: Served Korean Conflict June 1950 January
- **Lang1**:  Language Other Than English At Home
- **Looking**: Looking for Work
- **Marital**: Marital Stat.
- **May75880**: Served May 1975 to August 1980
- **Means**: Means of Transportation to Work 
- **Military**: Served May 1975 to August 1980
- **Mobility**: Mobility Stat. Lived Here on April 1, 19
- **Mobillim**: Mobility Limitation
- **Occup**: Occupation
- **Othrserv**: Served Any Other Time
- **Perscare**: Personal Care Limitation
- **POB**: Place of Birth
- **Poverty**: Pers. Poverty Stat.
- **Pwgt1**: Pers. Wgt
- **Ragechld**: Presence and Age of Own Chld.
- **Rearning**: Total Pers. Earnings
- **Relat1**: Rel. or Not Related or Grp. Qtrs.
- **Relat2**: Detailed Rel. Other Rel.
- **Remplpar**: Employment Stat. of Parents
- **Riders**: Vehicle Occupancy
- **Rlabor**: Employment Stat. Recode
- **Rownchld**: Own Child
- **Rpincome**: Total Pers. Inc. Signed
- **RPOB**: Place of Birth Recode
- **Rrelchld**: Related Child
- **Rspouse**: Married, Spouse Present/spouse Absent
- **Rvetserv**: Veteran Per. of Srvc.
- **School**: School Enrollment
- **Sept80**: Served September 1980 or Later
- **Sex**
- **Subfam1**: Subfam. Rel.
- **Subfam2**: Subfam. Number
- **Tmpabsnt**: Temp. Absence From Work
- **Travtime**: Travel Time to Work
- **Vietnam**: Served Vietnam Era August 1964 April 197
- **Week89**: Wks. Worked Last Yr. 1989
- **Work89**: Worked Last Yr. 1989
- **Worklwk**: Worked Last Week
- **WWII**: Served World War II September 1940 July
- **Yearsch**: Ed. Attainment
- **Yearwrk**: Yr. Last Worked
- **Yrsserv**: Yrs. of Active Duty Military Srvc.

https://rdrr.io/cran/rsubgroup/man/SDTaskConfig-class.html

```{r}
set.seed(2021)
data_sample <- sample_n(data, round(nrow(data)*0.1))
data_sample[] <- lapply(data_sample, factor) # the "[]" keeps the dataframe structure
col_names <- names(data_sample)
# to do it for some names in a vector named 'col_names'
data_sample[col_names] <- lapply(data_sample[col_names] , factor)
str(data_sample)
head(data_sample)
```

```{r}
old <- Sys.time()

print(old)

english = DiscoverSubgroups(data_sample, as.target("iEnglish", "4"),
                              new("SDTaskConfig",
                                  attributes=c("dAge",
                                               "dAncstry1",
                                               "dAncstry2",
                                               "iCitizen",
                                               "iClass", 
                                               "iImmigr",
                                               "dPOB", 
                                               "dPoverty",
                                               "iWork89",
                                               "iSex",
                                               "iYearsch",
                                               "iYearwrk")))
new <- Sys.time() - old
ToDataFrame(english)
print(new)
```


```{r}
old <- Sys.time()

print(old)

disabled = DiscoverSubgroups(data_sample, as.target("iDisabl1", "1"),
                              new("SDTaskConfig",
                                  attributes=c("dAge",
                                               "iCitizen",
                                               "iMilitary",
                                               "iWork89",
                                               "iWWII", 
                                               "dYrsserv",
                                               "iFeb55", 
                                               "iKorean",
                                               "dIndustry",
                                               "iMay75880",
                                               "iYearsch",
                                               "iYearwrk")))
new <- Sys.time() - old
ToDataFrame(disabled)
print(new)
```

```{r}
old <- Sys.time()

print(old)

class = DiscoverSubgroups(data_sample, as.target("iClass", "5"),
                              new("SDTaskConfig",
                                  attributes=c("dAncstry1",
                                               "dAncstry2",
                                               "iCitizen",
                                               "iDisabl1", 
                                               "iDisabl2",
                                               "iEnglish", 
                                               "iImmigr",
                                               "dIndustry",
                                               "iKorean",
                                               "iMilitary",
                                               "iMobility",
                                               "dOccup",
                                               "iVietnam",
                                               "iWWII",
                                               "iYearsch",
                                               "iRemplpar",
                                               "dPoverty",
                                               "dPOB",
                                               "iRvetserv")))
new <- Sys.time() - old
ToDataFrame(class)
print(new)
```

```{r}
old <- Sys.time()

print(old)

doctorate_ps = DiscoverSubgroups(data_sample, as.target("iYearsch", "17"),
                              new("SDTaskConfig",
                                  attributes=c("dAncstry1",
                                               "dAncstry2",
                                               "iClass",
                                               "dDepart",
                                               "iLang1",
                                               "dPoverty",
                                               "iCitizen",
                                               "iDisabl1", 
                                               "iDisabl2",
                                               "iEnglish", 
                                               "iImmigr",
                                               "dIndustry",
                                               "dOccup",
                                               "iRemplpar",
                                               "dPoverty",
                                               "dPOB",
                                               "iRvetserv",
                                               "iSex", 
                                               "dIncome1",
                                               "dIncome2",
                                               "dIncome3",
                                               "dIncome4",
                                               "dIncome5",
                                               "dIncome6",
                                               "dIncome7",
                                               "dIncome8", 
                                               "iFertil",
                                               "iMilitary",
                                               "iRelat1",
                                               "iRelat2")))
new <- Sys.time() - old
ToDataFrame(doctorate_ps)
print(new)
```



```{r}
old <- Sys.time()

print(old)

doctorate_ares = DiscoverSubgroups(data_sample, as.target("iYearsch", "17"),
                              new("SDTaskConfig",
                                  attributes=c("dAncstry1",
                                               "dAncstry2",
                                               "iClass",
                                               "dDepart",
                                               "iLang1",
                                               "dPoverty",
                                               "iCitizen",
                                               "iDisabl1", 
                                               "iDisabl2",
                                               "iEnglish", 
                                               "iImmigr",
                                               "dIndustry",
                                               "dOccup",
                                               "iRemplpar",
                                               "dPoverty",
                                               "dPOB",
                                               "iRvetserv",
                                               "iSex", 
                                               "dIncome1",
                                               "dIncome2",
                                               "dIncome3",
                                               "dIncome4",
                                               "dIncome5",
                                               "dIncome6",
                                               "dIncome7",
                                               "dIncome8", 
                                               "iFertil",
                                               "iMilitary",
                                               "iRelat1",
                                               "iRelat2"), qf='ares'))
new <- Sys.time() - old
ToDataFrame(doctorate_ares)
print(new)
```

```{r}
old <- Sys.time()

print(old)

doctorate_bsd = DiscoverSubgroups(data_sample, as.target("iYearsch", "17"),
                              new("SDTaskConfig",
                                  attributes=c("dAncstry1",
                                               "dAncstry2",
                                               "iClass",
                                               "dDepart",
                                               "iLang1",
                                               "dPoverty",
                                               "iCitizen",
                                               "iDisabl1", 
                                               "iDisabl2",
                                               "iEnglish", 
                                               "iImmigr",
                                               "dIndustry",
                                               "dOccup",
                                               "iRemplpar",
                                               "dPoverty",
                                               "dPOB",
                                               "iRvetserv",
                                               "iSex", 
                                               "dIncome1",
                                               "dIncome2",
                                               "dIncome3",
                                               "dIncome4",
                                               "dIncome5",
                                               "dIncome6",
                                               "dIncome7",
                                               "dIncome8", 
                                               "iFertil",
                                               "iMilitary",
                                               "iRelat1",
                                               "iRelat2"), method='bsd'))
new <- Sys.time() - old
ToDataFrame(doctorate_bsd)
print(new)
```