---
title: "Descubrimiento de subgrupos en el dataset *US Census Data*"
author: "Miruna Andreea Gheata, Miguel Rodríguez Gómez"
date: "3/16/2021"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
    df_print: paged
    number_sections: true
---

```{r}
# install.packages("fst")
library(fst)
data.filename = "USCensus1990.fst"
data <- read.fst("USCensus1990.fst")
```
```{r}
str(data)
```

- **Age**: Age Allocation Flag
- **Ancstry1**: First Ancestry Allocation Flag
- **Ancstry2**: Second Ancestry Allocation Flag
- **Avail**: Available for Work
- **Citizen**: Citizenship
- **Class**: Class of Worker
- **Depart**: Time of Departure for Work Hour and Minutes
- **Disabl1**:  Work Limitation Stat.
- **Disabl2**: Work Prevention Stat.
- **English**: Ability to Speak English
- **Feb55**: Served February 1955 July 1964
- **Fertil**: No. of Chld. Ever Born
- **Hispanic**: Detailed Hispanic Origin
- **Hour89**: Usual Hrs. Worked Per Week in 1989 Alloc
- **Hours**: Hrs. Worked Last Week Allocation Flag
- **Immigr**: Yr. of Entry
- **Income1**: Wages or Salary Inc. in 1989
- **Income2**: Nonfarm Self Employment Inc.
- **Income3**: Farm Self Employment Inc.
- **Income4**: Int., Dividends, and Net Rental Inc
- **Income5**: Soc. Sec Inc.
- **Income6**: Pub. Asst.
- **Income7**: Ret. Inc.
- **Income8**: All Other Inc.
- **Industry**: Ind.
- **Korean**: Served Korean Conflict June 1950 January
- **Lang1**:  Language Other Than English At Home
- **Looking**: Looking for Work
- **Marital**: Marital Stat.
- **May75880**: Served May 1975 to August 1980
- **Means**: Means of Transportation to Work 
- **Military**: Served May 1975 to August 1980
- **Mobility**: Mobility Stat. Lived Here on April 1, 19
- **Mobillim**: Mobility Limitation
- **Occup**: Occupation
- **Othrserv**: Served Any Other Time
- **Perscare**: Personal Care Limitation
- **POB**: Place of Birth
- **Poverty**: Pers. Poverty Stat.
- **Pwgt1**: Pers. Wgt
- **Ragechld**: Presence and Age of Own Chld.
- **Rearning**: Total Pers. Earnings
- **Relat1**: Rel. or Not Related or Grp. Qtrs.
- **Relat2**: Detailed Rel. Other Rel.
- **Remplpar**: Employment Stat. of Parents
- **Riders**: Vehicle Occupancy
- **Rlabor**: Employment Stat. Recode
- **Rownchld**: Own Child
- **Rpincome**: Total Pers. Inc. Signed
- **RPOB**: Place of Birth Recode
- **Rrelchld**: Related Child
- **Rspouse**: Married, Spouse Present/spouse Absent
- **Rvetserv**: Veteran Per. of Srvc.
- **School**: School Enrollment
- **Sept80**: Served September 1980 or Later
- **Sex**
- **Subfam1**: Subfam. Rel.
- **Subfam2**: Subfam. Number
- **Tmpabsnt**: Temp. Absence From Work
- **Travtime**: Travel Time to Work
- **Vietnam**: Served Vietnam Era August 1964 April 197
- **Week89**: Wks. Worked Last Yr. 1989
- **Work89**: Worked Last Yr. 1989
- **Worklwk**: Worked Last Week
- **WWII**: Served World War II September 1940 July
- **Yearsch**: Ed. Attainment
- **Yearwrk**: Yr. Last Worked
- **Yrsserv**: Yrs. of Active Duty Military Srvc.